---
title: "Using Openair Mapping Functions"
author: "Peter Levy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Openair Mapping Functions}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  fig.show='hold'
)
```
```{r, eval = FALSE, include = FALSE}
rmarkdown::render("vignettes/openairmaps.Rmd")
```

This vignette illustrates the use of `openairmaps` to produce a simple 
interactive leaflet maps showing weather station sites.


## Network map

The simplest function is simply to create a network map with the `network_map` 
function shown below

```{r}
here::i_am("vignettes/openairmaps.Rmd")
library(metamet)

fname_site <- here::here("data-raw/dt_site.csv")
dt_site <- fread(fname_site)
network_map(dt_site)
```

## Polar plot maps

We can also create interactive polar plot maps using `polar_map()`.
The function extracts the appropriate time, wind speed, and wind direction 
fields from a metamet object, and produces a leaflet-based polar map.
for a varible `var_name` chosen to be mapped.

```{r}
fname_dt <- here::here("data-raw/UK-AMO/UK-AMO_BM_dt_2026.csv")
  fname_meta <- here::here("data-raw/dt_meta.xlsx")
  fname_site <- here::here("data-raw/dt_site.csv")
  # half-hourly data
  mm <- metamet(
    dt = fname_dt,
    dt_meta = fname_meta,
    dt_site = fname_site,
    site_id = "UK-AMO"
  )
  polar_map(mm, var_name = "PA_4_1_1")
```
