---
title: "Workflow Example 1"
author: "Peter Levy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow Example 1}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  fig.show='hold'
)
```
```{r, eval = FALSE, include = FALSE}
rmarkdown::render("vignettes/workflow_example.Rmd")
```

This vignette illustrates the typical workflow for processing met data with 
`metamet`. The basic steps are to:

- read the observation data
- create a corresponding metadata table `dt_meta` for the observed variables 
- create a metadata table `dt_site` for each site with observations
- combine these into a single `metamet` object

## Example data

To illustrate, we will use some publicy available data from Whim Moss, available
from the [EIDC data centre](https://catalogue.ceh.ac.uk/documents/ba9ecad2-1740-41e6-8f73-b308340d49fe).
Metadata are available in the supporting documentation, but not in a 
machine-readable format, so we have to extract it manually the first time. 
Thereafter it is available within the `metamet` object for all future use.

Firstly, we load the `metamet` library, as well as the `here` library which 
simplifies specifying file paths.

```{r}
here::i_am("vignettes/workflow_example.Rmd")
library(metamet)
library(here)
```

### Observation data `dt`

Having downloaded the observation data, we can read it from a file and display 
a few rows.

```{r}
fname <- here("tests/testthat/data-raw/UK-WHM/whim_met_2002_2023.csv")
dt <- fread(fname)
dim(dt)
dt
```

The data consist of a timestamp column, and 13 variables observed every 15 
minutes from 2003 until 2023, giving `r nrow(dt)` rows and `r ncol(dt)` columns.

### Observation metadata `dt_meta`

```{r, include = FALSE}
fname <- here("data-raw/dt_meta.xlsx")
dt_meta <- setDT(readxl::read_excel(fname))

v_col <- c(
  "site",
  "name_dt",
  "name_local",
  "units_local",
  "type",
  "time_char_format",
  # "start_date",
  # "end_date",
  # "horizontal_id",
  # "vertical_id",
  # "replicate_id",
  # "gf_time",
  # "gf_era5",
  # "gf_night_zero",
  # "diff_ref_max",
  # "sensor_make",
  # "sensor_model",
  "range_min",
  "range_max",
  "name_era5",
  "units_era5",
  "imputation_method"
)
```

```{r}
knitr::kable(dt_meta[site == "UK-WHM", ..v_col], format = "html")
```

### Site data `dt_site`

The site metadata required is minimal. Any additional variables can be added, 
but at a minimum we require the site name, a uniquely identifying code `site`,
longitude, latitude (in degrees with a decimal fraction) and elevation (in m).
These are easily gleaned from the supporting documentation and could be entered
in excel, read in as a .csv text file, or entered directly in R as below.

```{r, fig.show='hold'}
dt_site <- data.table(
  site = "UK-WHM",
  long_name = "Whim Moss",
  lon = -3.27155,
  lat = -55.76566,
  elev = 316
)
dt_site
```

In practice, we are likely to have multiple sites as in the table below, and it
is easiest to append rows to a .csv or excel file as new sites are added.

```{r, fig.show='hold'}
fname <- here("data-raw/dt_site.csv")
dt_site <- fread(fname)
knitr::kable(dt_site, format = "html")
```

### Create `metamet` object

TBC