---
title: "Workflow Example 2 - Mutiple Sites"
author: "Peter Levy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow Example 2 - Mutiple Sites}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  fig.show='hold'
)
```

```{r, eval = FALSE, include = FALSE}
rmarkdown::render("vignettes/workflow_multisite.Rmd")
```

This vignette illustrates the typical workflow for quality control of met data 
from multiple sites simultaneously with `metamet`. We assume that the basic 
steps of reading the observation data, creating systematic metadata for the
variables and each site (described in [Workflow Example 1](workflow_example.html)).
This produces a single `metamet` object for each site.


## Example data

Here, we load data from three sites.

```{r}
here::i_am("vignettes/workflow_example.Rmd")
library(here)
library(testthat)
library(metamet)
```

### Observation data `dt`

Having downloaded the observation data, we can read it from a file and display 
a few rows.

```{r}
  mm_amo <- readRDS(
    file = here::here("data-raw/UK-AMO/UK-AMO_BM_mm_2023.rds")
  )
  mm_ebu <- readRDS(
    file = here::here("data-raw/UK-EBU/UK-EBU_BM_mm_2023.rds")
  )
  mm_whm <- readRDS(
    file = here::here("data-raw/UK-WHM/UK-WHM_BM_mm_2023.rds")
  )

  mm_amo <- subset_by_date(mm_amo, "2023-09-01", "2023-09-02")
  mm_ebu <- subset_by_date(mm_ebu, "2023-09-01", "2023-09-02")
  mm_whm <- subset_by_date(mm_whm, "2023-09-01", "2023-09-02")

  dim(mm_amo$dt)
  dim(mm_whm$dt)
  dim(mm_ebu$dt)

  mm_whm <- change_naming_convention(mm_whm, name_convention = "name_icos")

  mm_amo <- reshape_wide_to_long(mm_amo)
  mm_ebu <- reshape_wide_to_long(mm_ebu)
  mm_whm <- reshape_wide_to_long(mm_whm)

  dim(mm_amo$dt)
  dim(mm_ebu$dt)
  dim(mm_whm$dt)

  mm <- rbind_metamet(
    mm_amo,
    l_dt = list(mm_amo$dt, mm_ebu$dt, mm_whm$dt),
    l_dt_meta = list(mm_amo$dt_meta, mm_ebu$dt_meta, mm_whm$dt_meta),
    l_dt_site = list(mm_amo$dt_site, mm_ebu$dt_site, mm_whm$dt_site)
  )
  dim(mm$dt)
  names(mm$dt)
```

```{r}
  p <- ggplot(
    mm$dt[name_icos == "TS", ],
    aes(TIMESTAMP, value, colour = var_name)
  )
  p <- p + geom_line(aes(y = ref), colour = "black")
  p <- p + geom_point()
  p <- p + facet_wrap(~site)
  print(p)
```

```{r}
  p <- ggplot(
    mm$dt[name_icos == "PPFD_IN", ],
    aes(TIMESTAMP, value, colour = var_name)
  )
  p <- p + geom_line(aes(y = ref), colour = "black")
  p <- p + geom_line(alpha = 0.5)
  p <- p + facet_wrap(~site)
  print(p)
```

```{r}
  p <- ggplot(
    mm$dt[name_icos == "TA", ],
    aes(ref, value, colour = var_name)
  )
  p <- p + geom_abline()
  p <- p + geom_point()
  p <- p + facet_wrap(~site)
  print(p)
```
