---
title: "Workflow Example 2 - Multiple Sites"
author: "Peter Levy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow Example 2 - Multiple Sites}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  fig.show='hold'
)
```

```{r, eval = FALSE, include = FALSE}
rmarkdown::render("vignettes/workflow_multisite.Rmd")
```

This vignette illustrates the typical workflow for quality control of met data 
from multiple sites simultaneously with `metamet`. We assume that the basic 
steps have been carried out already: reading the raw observation data, creating 
systematic metadata for the variables and each site (described 
in [Workflow Example 1](workflow_example.html)).
This produces a single `metamet` object for each site.

First, we load the `metamet` library, and read the data for each of three sites
from file. 

```{r}
here::i_am("vignettes/workflow_example.Rmd")
library(here)
library(metamet)

mm_amo <- readRDS(
  file = here::here("data-raw/UK-AMO/UK-AMO_BM_mm_2023.rds")
)
mm_ebu <- readRDS(
  file = here::here("data-raw/UK-EBU/UK-EBU_BM_mm_2023.rds")
)
mm_whm <- readRDS(
  file = here::here("data-raw/UK-WHM/UK-WHM_BM_mm_2023.rds")
)
```

This gives us all the half-hourly data for 2023 from each site.  If we want to
process a shorter time period, we can subset as required with `subset_by_date`.
Here we look at two days just for speed.


```{r}
mm_amo <- subset_by_date(mm_amo, "2023-09-01", "2023-09-03")
mm_ebu <- subset_by_date(mm_ebu, "2023-09-01", "2023-09-03")
mm_whm <- subset_by_date(mm_whm, "2023-09-01", "2023-09-03")
```

In order to combine data from different sites in a meningful way, they all need
to use the same naming convention. Here we convert two of the sites to the ICOS
convention using the `change_naming_convention` function below (UK-AMO data are
already produced in this form).

```{r}
mm_ebu <- change_naming_convention(mm_ebu, name_convention = "name_icos")
mm_whm <- change_naming_convention(mm_whm, name_convention = "name_icos")
```

Although the base names of variable are now standardised across sites, the 
specific variables measured will vary across sites. For example, one site may
have two replicate measurements of air temperature TA_4_1_1 and TA_5_1_1, while
another has a single replicate TA_1_1_1. These cannot be combined as a single 
variable (or related variables) in wide format. Also, wide format would require
columns for the full set of variables found across all sites, many of which will
be empty for all sites except one. The efficient solution is to convert to long
format, so all values are in a single column, with additional columns to 
identify the site, timestamp, varaiable type and specific varaiable name. We do
this with the `reshape_wide_to_long` function, shown below.

```{r}
mm_amo <- reshape_wide_to_long(mm_amo)
mm_ebu <- reshape_wide_to_long(mm_ebu)
mm_whm <- reshape_wide_to_long(mm_whm)
```

We can now see the structure of UK-AMO data 

```{r}
mm_amo$dt
```
and see it is identical to the structure of UK-EBU (and UK-WHM) data.
```{r}
mm_ebu$dt
```

Given this structure, we can simply append all the rows for all data tables to
create a single `metamet` object.

```{r}
mm <- rbind_metamet(
  mm_amo,
  l_dt = list(mm_amo$dt, mm_ebu$dt, mm_whm$dt),
  l_dt_meta = list(mm_amo$dt_meta, mm_ebu$dt_meta, mm_whm$dt_meta),
  l_dt_site = list(mm_amo$dt_site, mm_ebu$dt_site, mm_whm$dt_site)
)
```

We can now plot all the variables of a given type for all the types, identifying
site by colour or separate panels (facets). Below we plot soil temperature 
against time; the solid black line shows the reference data, which in this case 
is ERA5 reanalysis data for the grid cell containing the site.

```{r}
p <- ggplot(
  mm$dt[name_icos == "TS", ],
  aes(TIMESTAMP, value, colour = var_name)
)
p <- p + geom_line(aes(y = ref), colour = "black")
p <- p + geom_point()
p <- p + facet_wrap(~site)
print(p)
```

Below we plot PPFD (photosynthetic photon flux density, commonly 'PAR')
against time; the solid black line shows the ERA5 reference data.

```{r}
p <- ggplot(
  mm$dt[name_icos == "PPFD_IN", ],
  aes(TIMESTAMP, value, colour = var_name)
)
p <- p + geom_line(aes(y = ref), colour = "black")
p <- p + geom_line(alpha = 1.0)
p <- p + facet_wrap(~site)
print(p)
```

We can also plot all variable against the reference (ERA5) data to check for
anomalous deviations from the expected relationship.

```{r}
p <- ggplot(
  mm$dt[name_icos == "TA", ],
  aes(ref, value, colour = var_name)
)
p <- p + geom_abline()
p <- p + geom_point()
p <- p + facet_wrap(~site)
print(p)
```
